### 2013-03-26 doc/sosp13/intro.tex
lots of edits. mostly to comm
a couple more changes. 	modified:   intro.tex

\noindent{\bf High Latency} To tolerate latency, data parallel applications make explicit
their regular, predictable communications so as to minimize interference with computation.
In contrast, irregular application tasks encounter remote references dynamically during
execution and must resolve them before making further progress.  The latency of
commodity networks is anywhere from one to hundreds of microseconds,
far more than can be tolerated via the hyperthrading available in x86 processors.
Consequently, even with RDMA, processor prefetching and caching hardware alone is inadequate
to ensure pipeline utilization in the presence of high latency networks.

>>>>

\noindent{\bf High Latency} To tolerate latency, data parallel applications make explicit
their regular, predictable communications so as to minimize interference with computation.
In contrast, irregular application tasks encounter remote references dynamically during
execution and must resolve them before making further progress.  Latency of
commodity networks runs anywhere from one to hundreds of microseconds,
far more than can be tolerated via the hyperthrading available in x86 processors.
Consequently, even with RDMA, processors' prefetching and caching hardware alone is inadequate
to prevent diminishing pipeline utilization as irregular applications are scaled up using
commodity networks.
